Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-08-23 paper.Rnw
mini edits from the meeting

\hh{All runs of LIME in this paper are executed in}
a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}. 
The forked version \hh{is functionally indistinguishable from Pedersen's implementation but it} allows us to export internal values \hh{relevant for an assessment of the explainer}. 
The R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid} (\Sexpr{packageVersion("limeaid")}) implements diagnostic plots based on the output of the altered version of `lime`.

>>>>

\hh{All runs of LIME in this paper are executed in}
a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}. 
The forked version \hh{is functionally indistinguishable from Pedersen's implementation but it} allows us to export internal values \hh{relevant for an assessment of the explainer}. 
The R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid} (\Sexpr{packageVersion("limeaid")}) implements diagnostic plots based on the output of the altered version of \emph{lime}.
